---
title: "Lab Exercise#2 Bagilidad"
author: "Bagilidad Ace"
date: "2024-02-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



PRODUCT 1
```{r}

library(polite)
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[3:12]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[3:12]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[4:13]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Tall/product-reviews/B088XZH343/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Tall/product-reviews/B088XZH343/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Tall/product-reviews/B088XZH343/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Tall/product-reviews/B088XZH343/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Tall/product-reviews/B088XZH343/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview1 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview1)


```



PRODUCT 2
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Smooth-Lamb/product-reviews/B01KWHVGFS/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Smooth-Lamb/product-reviews/B01KWHVGFS/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Smooth-Lamb/product-reviews/B01KWHVGFS/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Smooth-Lamb/product-reviews/B01KWHVGFS/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Smooth-Lamb/product-reviews/B01KWHVGFS/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview2 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview2)


```


PRODUCT 3
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Jack-Jones-12165203-Mens-JJERUSH/product-reviews/B084N24CD5/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Jack-Jones-12165203-Mens-JJERUSH/product-reviews/B084N24CD5/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Jack-Jones-12165203-Mens-JJERUSH/product-reviews/B084N24CD5/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Jack-Jones-12165203-Mens-JJERUSH/product-reviews/B084N24CD5/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Jack-Jones-12165203-Mens-JJERUSH/product-reviews/B084N24CD5/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview3 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview3)

```

PRODUCT 4
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[3:12]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[3:12]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[4:13]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Dickies-Mens-Insulated-Eisenhower-Jacket/product-reviews/B0C6P1MQ3C/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=1"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Dickies-Mens-Insulated-Eisenhower-Jacket/product-reviews/B0C6P1MQ3C/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Dickies-Mens-Insulated-Eisenhower-Jacket/product-reviews/B0C6P1MQ3C/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Dickies-Mens-Insulated-Eisenhower-Jacket/product-reviews/B0C6P1MQ3C/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Dickies-Mens-Insulated-Eisenhower-Jacket/product-reviews/B0C6P1MQ3C/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview4 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview4)



```

PRODUCT 5
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Helly-Hansen-Daybreaker-Fleece-Vest/product-reviews/B07BZLT5Y7/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Helly-Hansen-Daybreaker-Fleece-Vest/product-reviews/B07BZLT5Y7/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Helly-Hansen-Daybreaker-Fleece-Vest/product-reviews/B07BZLT5Y7/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Helly-Hansen-Daybreaker-Fleece-Vest/product-reviews/B07BZLT5Y7/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Helly-Hansen-Daybreaker-Fleece-Vest/product-reviews/B07BZLT5Y7/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview5 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview5)


```

PRODUCT 6
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[2:11]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/CARHARTT-102286-001-Carhartt-Mens-Gilliam/product-reviews/B0891MTMHM/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/CARHARTT-102286-001-Carhartt-Mens-Gilliam/product-reviews/B0891MTMHM/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/CARHARTT-102286-001-Carhartt-Mens-Gilliam/product-reviews/B0891MTMHM/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/CARHARTT-102286-001-Carhartt-Mens-Gilliam/product-reviews/B0891MTMHM/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/CARHARTT-102286-001-Carhartt-Mens-Gilliam/product-reviews/B0891MTMHM/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview6 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview6)



```
PRODUCT 7
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Champion-V1012-ChampionChampion/product-reviews/B078GGN89P/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Champion-V1012-ChampionChampion/product-reviews/B078GGN89P/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Champion-V1012-ChampionChampion/product-reviews/B078GGN89P/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Champion-V1012-ChampionChampion/product-reviews/B078GGN89P/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Champion-V1012-ChampionChampion/product-reviews/B078GGN89P/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview7 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview7)


```

PRODUCT 8
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Leatherick-Mens-Leather-Waistcoat-Black/product-reviews/B0BR48ZSQ1/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Leatherick-Mens-Leather-Waistcoat-Black/product-reviews/B0BR48ZSQ1/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Leatherick-Mens-Leather-Waistcoat-Black/product-reviews/B0BR48ZSQ1/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Leatherick-Mens-Leather-Waistcoat-Black/product-reviews/B0BR48ZSQ1/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Leatherick-Mens-Leather-Waistcoat-Black/product-reviews/B0BR48ZSQ1/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview8 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview8)


```

PRODUCT 9
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Wrangler-Rustic-Sherpa-Lined-Jacket/product-reviews/B07HX17XXJ/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Wrangler-Rustic-Sherpa-Lined-Jacket/product-reviews/B07HX17XXJ/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Wrangler-Rustic-Sherpa-Lined-Jacket/product-reviews/B07HX17XXJ/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Wrangler-Rustic-Sherpa-Lined-Jacket/product-reviews/B07HX17XXJ/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Wrangler-Rustic-Sherpa-Lined-Jacket/product-reviews/B07HX17XXJ/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview9 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview9)

```

PRODUCT 10
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Tommy-Hilfiger-Waterproof-Breathable-Hooded/product-reviews/B079TD7DK9/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Tommy-Hilfiger-Waterproof-Breathable-Hooded/product-reviews/B079TD7DK9/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Tommy-Hilfiger-Waterproof-Breathable-Hooded/product-reviews/B079TD7DK9/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Tommy-Hilfiger-Waterproof-Breathable-Hooded/product-reviews/B079TD7DK9/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Tommy-Hilfiger-Waterproof-Breathable-Hooded/product-reviews/B079TD7DK9/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview10 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview10)



```


PRODUCT 11
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/CARHARTT-102208-Carhartt-Gilliam-Jacket/product-reviews/B0CQP25Y66/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/CARHARTT-102208-Carhartt-Gilliam-Jacket/product-reviews/B0CQP25Y66/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/CARHARTT-102208-Carhartt-Gilliam-Jacket/product-reviews/B0CQP25Y66/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/CARHARTT-102208-Carhartt-Gilliam-Jacket/product-reviews/B0CQP25Y66/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/CARHARTT-102208-Carhartt-Gilliam-Jacket/product-reviews/B0CQP25Y66/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview11 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview11)



```


PRODUCT 12
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[3:12]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[3:12]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[4:13]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Legendary-Whitetails-6575-P/product-reviews/B07XM9KR49/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Legendary-Whitetails-6575-P/product-reviews/B07XM9KR49/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Legendary-Whitetails-6575-P/product-reviews/B07XM9KR49/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Legendary-Whitetails-6575-P/product-reviews/B07XM9KR49/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Legendary-Whitetails-6575-P/product-reviews/B07XM9KR49/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview12 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview12)





```


PRODUCT 13

```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[3:12]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[3:12]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[4:13]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Wrangler-080081-Mens-Unlined/product-reviews/B07CYN1MY2/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Wrangler-080081-Mens-Unlined/product-reviews/B07CYN1MY2/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Wrangler-080081-Mens-Unlined/product-reviews/B07CYN1MY2/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Wrangler-080081-Mens-Unlined/product-reviews/B07CYN1MY2/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Wrangler-080081-Mens-Unlined/product-reviews/B07CYN1MY2/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview13 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview13)




```

PRODUCT 14
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[1:10]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Full/product-reviews/B073JHC787/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Full/product-reviews/B073JHC787/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Full/product-reviews/B073JHC787/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Full/product-reviews/B073JHC787/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Full/product-reviews/B073JHC787/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview14 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview14)





```

PRODUCT 15
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Frogg-Toggs-Pilot-Guide-Jacket/product-reviews/B07G3WJY5D/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Frogg-Toggs-Pilot-Guide-Jacket/product-reviews/B07G3WJY5D/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Frogg-Toggs-Pilot-Guide-Jacket/product-reviews/B07G3WJY5D/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Frogg-Toggs-Pilot-Guide-Jacket/product-reviews/B07G3WJY5D/ref=cm_cr_arp_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Frogg-Toggs-Pilot-Guide-Jacket/product-reviews/B07G3WJY5D/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview15 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview15)


```
PRODUCT 16
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Polar-Fleece/product-reviews/B0757YPPN9/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Polar-Fleece/product-reviews/B0757YPPN9/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Polar-Fleece/product-reviews/B0757YPPN9/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Polar-Fleece/product-reviews/B0757YPPN9/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Polar-Fleece/product-reviews/B0757YPPN9/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview16 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview16)





```


PRODUCT 17
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Ergodyne-Chill-Its-Evaporative-Cooling-Vest/product-reviews/B09JW9C2FX/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Ergodyne-Chill-Its-Evaporative-Cooling-Vest/product-reviews/B09JW9C2FX/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Ergodyne-Chill-Its-Evaporative-Cooling-Vest/product-reviews/B09JW9C2FX/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Ergodyne-Chill-Its-Evaporative-Cooling-Vest/product-reviews/B09JW9C2FX/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Ergodyne-Chill-Its-Evaporative-Cooling-Vest/product-reviews/B09JW9C2FX/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview17 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview17)



```

PRODUCT 18 
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Columbia-Mens-Vest-Powder-Pass/product-reviews/B088YMHQSV/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Columbia-Mens-Vest-Powder-Pass/product-reviews/B088YMHQSV/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Columbia-Mens-Vest-Powder-Pass/product-reviews/B088YMHQSV/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Columbia-Mens-Vest-Powder-Pass/product-reviews/B088YMHQSV/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Columbia-Mens-Vest-Powder-Pass/product-reviews/B088YMHQSV/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview18 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview18)





```



PRODUCT 19
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Full/product-reviews/B079SNXPQ2/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Full/product-reviews/B079SNXPQ2/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Full/product-reviews/B079SNXPQ2/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Full/product-reviews/B079SNXPQ2/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Full/product-reviews/B079SNXPQ2/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview19 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview19)




```



PRODUCT 20
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens/product-reviews/B07GFTHWPZ/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens/product-reviews/B07GFTHWPZ/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens/product-reviews/B07GFTHWPZ/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens/product-reviews/B07GFTHWPZ/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens/product-reviews/B07GFTHWPZ/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview20 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview20)


```



PRODUCT 21
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[1:10]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Brandit-Mens-Summer-Windbreaker-Woodland/product-reviews/B082956H26/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Brandit-Mens-Summer-Windbreaker-Woodland/product-reviews/B082956H26/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Brandit-Mens-Summer-Windbreaker-Woodland/product-reviews/B082956H26/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Brandit-Mens-Summer-Windbreaker-Woodland/product-reviews/B082956H26/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Brandit-Mens-Summer-Windbreaker-Woodland/product-reviews/B082956H26/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview21 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview21)


```


PRODUCT 22
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Ergodyne-Chill-Its-Evaporative-Cooling-Vest/product-reviews/B09JW9C2FX/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Ergodyne-Chill-Its-Evaporative-Cooling-Vest/product-reviews/B09JW9C2FX/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Ergodyne-Chill-Its-Evaporative-Cooling-Vest/product-reviews/B09JW9C2FX/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Ergodyne-Chill-Its-Evaporative-Cooling-Vest/product-reviews/B09JW9C2FX/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Ergodyne-Chill-Its-Evaporative-Cooling-Vest/product-reviews/B09JW9C2FX/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview22 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview22)


```


PRODUCT 23
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[2:11]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/LONDON-FOG-Mens/product-reviews/B0CQYCR5ZG/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/LONDON-FOG-Mens/product-reviews/B0CQYCR5ZG/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/LONDON-FOG-Mens/product-reviews/B0CQYCR5ZG/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/LONDON-FOG-Mens/product-reviews/B0CQYCR5ZG/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/LONDON-FOG-Mens/product-reviews/B0CQYCR5ZG/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview23 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview23)

```


PRODUCT 24
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/THE-NORTH-FACE-Mens-Aconcagua/product-reviews/B0C78QDGZR/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/THE-NORTH-FACE-Mens-Aconcagua/product-reviews/B0C78QDGZR/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/THE-NORTH-FACE-Mens-Aconcagua/product-reviews/B0C78QDGZR/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/THE-NORTH-FACE-Mens-Aconcagua/product-reviews/B0C78QDGZR/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/THE-NORTH-FACE-Mens-Aconcagua/product-reviews/B0C78QDGZR/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview24 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview24)


```


PRODUCT 25
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Polar-Fleece/product-reviews/B0757YPPN9/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Polar-Fleece/product-reviews/B0757YPPN9/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Polar-Fleece/product-reviews/B0757YPPN9/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Polar-Fleece/product-reviews/B0757YPPN9/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Tommy-Hilfiger-Mens-Polar-Fleece/product-reviews/B0757YPPN9/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview25 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview25)

```



PRODUCT 26
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/DarcChic-Gothic-Tailcoat-Steampunk-Victorian/product-reviews/B07K2RFPZC/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/DarcChic-Gothic-Tailcoat-Steampunk-Victorian/product-reviews/B07K2RFPZC/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/DarcChic-Gothic-Tailcoat-Steampunk-Victorian/product-reviews/B07K2RFPZC/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/DarcChic-Gothic-Tailcoat-Steampunk-Victorian/product-reviews/B07K2RFPZC/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/DarcChic-Gothic-Tailcoat-Steampunk-Victorian/product-reviews/B07K2RFPZC/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview26 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview26)


```



PRODUCT 27
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Legendary-Whitetails-Mens-Tough-Canvas/product-reviews/B0846PX1G2/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Legendary-Whitetails-Mens-Tough-Canvas/product-reviews/B0846PX1G2/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Legendary-Whitetails-Mens-Tough-Canvas/product-reviews/B0846PX1G2/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Legendary-Whitetails-Mens-Tough-Canvas/product-reviews/B0846PX1G2/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Legendary-Whitetails-Mens-Tough-Canvas/product-reviews/B0846PX1G2/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview27 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview27)




```




PRODUCT 28
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Gihuo-Lightweight-Fishing-Travel-Safari/product-reviews/B08MT6WNKG/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/Gihuo-Lightweight-Fishing-Travel-Safari/product-reviews/B08MT6WNKG/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Gihuo-Lightweight-Fishing-Travel-Safari/product-reviews/B08MT6WNKG/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Gihuo-Lightweight-Fishing-Travel-Safari/product-reviews/B08MT6WNKG/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Gihuo-Lightweight-Fishing-Travel-Safari/product-reviews/B08MT6WNKG/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview28 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview28)




```



PRODUCT 29
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/ZENTHACE-Sherpa-Fleece-Flannel-Jacket/product-reviews/B0CM5J6MHW/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)

link2 <- "https://www.amazon.com.au/ZENTHACE-Sherpa-Fleece-Flannel-Jacket/product-reviews/B0CM5J6MHW/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/ZENTHACE-Sherpa-Fleece-Flannel-Jacket/product-reviews/B0CM5J6MHW/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/ZENTHACE-Sherpa-Fleece-Flannel-Jacket/product-reviews/B0CM5J6MHW/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/ZENTHACE-Sherpa-Fleece-Flannel-Jacket/product-reviews/B0CM5J6MHW/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview29 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview29)



```




PRODUCT 30
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Cutter-Buck-Clique-Full-Zip-Microfleece/product-reviews/B0CN7NRFJP/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Cutter-Buck-Clique-Full-Zip-Microfleece/product-reviews/B0CN7NRFJP/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Cutter-Buck-Clique-Full-Zip-Microfleece/product-reviews/B0CN7NRFJP/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Cutter-Buck-Clique-Full-Zip-Microfleece/product-reviews/B0CN7NRFJP/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Cutter-Buck-Clique-Full-Zip-Microfleece/product-reviews/B0CN7NRFJP/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview30 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview30)



```




PRODUCT 31
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Dickies-Mens-Diamond-Quilted-Nylon/product-reviews/B07BZQGWPX/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Dickies-Mens-Diamond-Quilted-Nylon/product-reviews/B07BZQGWPX/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Dickies-Mens-Diamond-Quilted-Nylon/product-reviews/B07BZQGWPX/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Dickies-Mens-Diamond-Quilted-Nylon/product-reviews/B07BZQGWPX/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Dickies-Mens-Diamond-Quilted-Nylon/product-reviews/B07BZQGWPX/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview31 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview31)


```
PRODUCT 32
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Club-Fleece-Lined-Windbreaker-Jacket/product-reviews/B09YHF53X4/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Club-Fleece-Lined-Windbreaker-Jacket/product-reviews/B09YHF53X4/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Club-Fleece-Lined-Windbreaker-Jacket/product-reviews/B09YHF53X4/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Club-Fleece-Lined-Windbreaker-Jacket/product-reviews/B09YHF53X4/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Club-Fleece-Lined-Windbreaker-Jacket/product-reviews/B09YHF53X4/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview32 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview32)


```




PRODUCT 33
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/TRAILSIDE-SUPPLY-CO-Medium-Weight-Water-Repellent/product-reviews/B07KVG822B/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/TRAILSIDE-SUPPLY-CO-Medium-Weight-Water-Repellent/product-reviews/B07KVG822B/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/TRAILSIDE-SUPPLY-CO-Medium-Weight-Water-Repellent/product-reviews/B07KVG822B/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/TRAILSIDE-SUPPLY-CO-Medium-Weight-Water-Repellent/product-reviews/B07KVG822B/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/TRAILSIDE-SUPPLY-CO-Medium-Weight-Water-Repellent/product-reviews/B07KVG822B/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview33 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview33)


```



PRODUCT 34
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Dickies-Big-Tall-Sanded-Sherpa-Hooded/product-reviews/B07JGDXHWX/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Dickies-Big-Tall-Sanded-Sherpa-Hooded/product-reviews/B07JGDXHWX/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Dickies-Big-Tall-Sanded-Sherpa-Hooded/product-reviews/B07JGDXHWX/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Dickies-Big-Tall-Sanded-Sherpa-Hooded/product-reviews/B07JGDXHWX/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Dickies-Big-Tall-Sanded-Sherpa-Hooded/product-reviews/B07JGDXHWX/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview34 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview34)


```




PRODUCT 35
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[2:11]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Barber-Jacket-Stylist-Grooming-Vintage/product-reviews/B07Z3VXBCZ/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Barber-Jacket-Stylist-Grooming-Vintage/product-reviews/B07Z3VXBCZ/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Barber-Jacket-Stylist-Grooming-Vintage/product-reviews/B07Z3VXBCZ/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Barber-Jacket-Stylist-Grooming-Vintage/product-reviews/B07Z3VXBCZ/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Barber-Jacket-Stylist-Grooming-Vintage/product-reviews/B07Z3VXBCZ/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview35 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview35)


```





PRODUCT 36

```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Wrangler-Western-Style-Lined-Jacket/product-reviews/B00CYAP8OC/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Wrangler-Western-Style-Lined-Jacket/product-reviews/B00CYAP8OC/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Wrangler-Western-Style-Lined-Jacket/product-reviews/B00CYAP8OC/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Wrangler-Western-Style-Lined-Jacket/product-reviews/B00CYAP8OC/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Wrangler-Western-Style-Lined-Jacket/product-reviews/B00CYAP8OC/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview36 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview36)


```




PRODUCT 37
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/ZENTHACE-Washed-Arctic-Quilt-Utility-Rugged/product-reviews/B082V7HR7F/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/ZENTHACE-Washed-Arctic-Quilt-Utility-Rugged/product-reviews/B082V7HR7F/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/ZENTHACE-Washed-Arctic-Quilt-Utility-Rugged/product-reviews/B082V7HR7F/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/ZENTHACE-Washed-Arctic-Quilt-Utility-Rugged/product-reviews/B082V7HR7F/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/ZENTHACE-Washed-Arctic-Quilt-Utility-Rugged/product-reviews/B082V7HR7F/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview37 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview37)


```




PRODUCT 38
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Charles-River-Apparel-Pack-N-Go-Windbreaker/product-reviews/B00JGL923K/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Charles-River-Apparel-Pack-N-Go-Windbreaker/product-reviews/B00JGL923K/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Charles-River-Apparel-Pack-N-Go-Windbreaker/product-reviews/B00JGL923K/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Charles-River-Apparel-Pack-N-Go-Windbreaker/product-reviews/B00JGL923K/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Charles-River-Apparel-Pack-N-Go-Windbreaker/product-reviews/B00JGL923K/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview38 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview38)


```



PRODUCT 39
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/CARHARTT-102286-001-Mens-Gilliam-Vest/product-reviews/B08D62BQ1Q/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/CARHARTT-102286-001-Mens-Gilliam-Vest/product-reviews/B08D62BQ1Q/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/CARHARTT-102286-001-Mens-Gilliam-Vest/product-reviews/B08D62BQ1Q/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/CARHARTT-102286-001-Mens-Gilliam-Vest/product-reviews/B08D62BQ1Q/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/CARHARTT-102286-001-Mens-Gilliam-Vest/product-reviews/B08D62BQ1Q/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview39 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview39)


```



PRODUCT 40
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Columbia-1519151-Mens-Cathedral-Peak/product-reviews/B07YNL4GBR/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Columbia-1519151-Mens-Cathedral-Peak/product-reviews/B07YNL4GBR/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Columbia-1519151-Mens-Cathedral-Peak/product-reviews/B07YNL4GBR/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Columbia-1519151-Mens-Cathedral-Peak/product-reviews/B07YNL4GBR/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Columbia-1519151-Mens-Cathedral-Peak/product-reviews/B07YNL4GBR/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview40 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview40)


```


PRODUCT 41
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Tall/product-reviews/B079SVH8QR/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Tall/product-reviews/B079SVH8QR/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Tall/product-reviews/B079SVH8QR/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Tall/product-reviews/B079SVH8QR/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Columbia-Mens-Steens-Mountain-Tall/product-reviews/B079SVH8QR/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview41 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview41)


```



PRODUCT 42
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/North-Face-Mens-Resolve-Jacket/product-reviews/B077QNCCJQ/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/North-Face-Mens-Resolve-Jacket/product-reviews/B077QNCCJQ/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/North-Face-Mens-Resolve-Jacket/product-reviews/B077QNCCJQ/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/North-Face-Mens-Resolve-Jacket/product-reviews/B077QNCCJQ/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/North-Face-Mens-Resolve-Jacket/product-reviews/B077QNCCJQ/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview42 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview42)


```



PRODUCT 43
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Leather-EL5315-Motorcycle-Riding-Regular/product-reviews/B00IWHHRY0/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Leather-EL5315-Motorcycle-Riding-Regular/product-reviews/B00IWHHRY0/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Leather-EL5315-Motorcycle-Riding-Regular/product-reviews/B00IWHHRY0/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Leather-EL5315-Motorcycle-Riding-Regular/product-reviews/B00IWHHRY0/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Leather-EL5315-Motorcycle-Riding-Regular/product-reviews/B00IWHHRY0/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview43 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview43)


```


PRODUCT 44
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Brandit-3110-2-Mens-CWU-Jacket/product-reviews/B089TF592K/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Brandit-3110-2-Mens-CWU-Jacket/product-reviews/B089TF592K/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Brandit-3110-2-Mens-CWU-Jacket/product-reviews/B089TF592K/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Brandit-3110-2-Mens-CWU-Jacket/product-reviews/B089TF592K/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Brandit-3110-2-Mens-CWU-Jacket/product-reviews/B089TF592K/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview44 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview44)


```



PRODUCT 45
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Stockerpoint-Mens-Weste-Ricardo-Trachtenwesten/product-reviews/B088YQ79PJ/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Stockerpoint-Mens-Weste-Ricardo-Trachtenwesten/product-reviews/B088YQ79PJ/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Stockerpoint-Mens-Weste-Ricardo-Trachtenwesten/product-reviews/B088YQ79PJ/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Stockerpoint-Mens-Weste-Ricardo-Trachtenwesten/product-reviews/B088YQ79PJ/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Stockerpoint-Mens-Weste-Ricardo-Trachtenwesten/product-reviews/B088YQ79PJ/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview45 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview45)


```



PRODUCT 46
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Columbia-Mens-Fast-Trek-Fleece/product-reviews/B0CRW2FSN9/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Columbia-Mens-Fast-Trek-Fleece/product-reviews/B0CRW2FSN9/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Columbia-Mens-Fast-Trek-Fleece/product-reviews/B0CRW2FSN9/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Columbia-Mens-Fast-Trek-Fleece/product-reviews/B0CRW2FSN9/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Columbia-Mens-Fast-Trek-Fleece/product-reviews/B0CRW2FSN9/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview46 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview46)


```



PRODUCT 47
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[1:10]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Columbia-Mens-Jackets-Black-Large/product-reviews/B072R1QZB3/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Columbia-Mens-Jackets-Black-Large/product-reviews/B072R1QZB3/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Columbia-Mens-Jackets-Black-Large/product-reviews/B072R1QZB3/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Columbia-Mens-Jackets-Black-Large/product-reviews/B072R1QZB3/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Columbia-Mens-Jackets-Black-Large/product-reviews/B072R1QZB3/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview47 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview47)


```



PRODUCT 48

```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Betty-Dain-Premier-Barber-Jacket/product-reviews/B007NIQUME/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Betty-Dain-Premier-Barber-Jacket/product-reviews/B007NIQUME/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Betty-Dain-Premier-Barber-Jacket/product-reviews/B007NIQUME/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Betty-Dain-Premier-Barber-Jacket/product-reviews/B007NIQUME/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Betty-Dain-Premier-Barber-Jacket/product-reviews/B007NIQUME/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview48 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview48)


```



PRODUCT 49
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Red-Kap-Zip-Front-Smock-Sleeve/product-reviews/B007FVWIC0/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Red-Kap-Zip-Front-Smock-Sleeve/product-reviews/B007FVWIC0/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Red-Kap-Zip-Front-Smock-Sleeve/product-reviews/B007FVWIC0/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Red-Kap-Zip-Front-Smock-Sleeve/product-reviews/B007FVWIC0/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Red-Kap-Zip-Front-Smock-Sleeve/product-reviews/B007FVWIC0/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview49 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview49)


```




PRODUCT 50
```{r}
library(httr)
library(rvest)
library(selectr)

category <- "Mens Jackets"

scrapingNodes <- function(session, HTMLnodes) {
  session %>% scrape() %>% html_nodes(HTMLnodes) %>% html_text()
}

prodDetails <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")

  Sys.sleep(7) 

  Product <- scrapingNodes(session, "h1.a-size-large.a-text-ellipsis")
  prodReviewer <- scrapingNodes(session, "span.a-profile-name")[1:10]
  prodReview <- scrapingNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
  ReviewerType <- scrapingNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  RevDate <- scrapingNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  prodRatings <- scrapingNodes(session, "span.a-icon-alt")[2:11]

  JacketProd <- data.frame( Category = category,
                           ProductName = Product,
                           Reviewer = prodReviewer,
                           Review = prodReview,
                           TypeOfReviewer = ReviewerType,
                           ReviewDate = RevDate,
                           Rating = prodRatings)
  return(JacketProd)
}


link1 <- "https://www.amazon.com.au/Red-Kap-Pocket-Quilt-Lined-Jacket/product-reviews/B004HCC3CA/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
page1 <- prodDetails(link1)


link2 <- "https://www.amazon.com.au/Red-Kap-Pocket-Quilt-Lined-Jacket/product-reviews/B004HCC3CA/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
page2 <- prodDetails(link2)

link3 <- "https://www.amazon.com.au/Red-Kap-Pocket-Quilt-Lined-Jacket/product-reviews/B004HCC3CA/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
page3 <- prodDetails(link3)

link4 <- "https://www.amazon.com.au/Red-Kap-Pocket-Quilt-Lined-Jacket/product-reviews/B004HCC3CA/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
page4 <- prodDetails(link4)


link5 <- "https://www.amazon.com.au/Red-Kap-Pocket-Quilt-Lined-Jacket/product-reviews/B004HCC3CA/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
page5 <- prodDetails(link5)


ProductReview50 <- rbind(page1, page2, page3,page4,page5)

#view(ProductReview50)


```


EMERGE ALL PRODUCTS
```{r}
AllProducts <-rbind(ProductReview1,
                     ProductReview2,
                     ProductReview3,
                     ProductReview4,
                     ProductReview5,
                     ProductReview6,
                     ProductReview7,
                     ProductReview8,
                     ProductReview9,
                     ProductReview10,
                     ProductReview11,
                     ProductReview12,
                     ProductReview13,
                     ProductReview14,
                     ProductReview15,
                     ProductReview16,
                     ProductReview17,
                     ProductReview18,
                     ProductReview19,
                     ProductReview20,
                     ProductReview21,
                     ProductReview22,
                     ProductReview23,
                     ProductReview24,
                     ProductReview25,
                     ProductReview26,
                     ProductReview27,
                     ProductReview28,
                     ProductReview29,
                     ProductReview30,
                     ProductReview31,
                     ProductReview32,
                     ProductReview33,
                     ProductReview34,
                     ProductReview35,
                     ProductReview36,
                     ProductReview37,
                     ProductReview38,
                     ProductReview39,
                     ProductReview40,
                     ProductReview41,
                     ProductReview42,
                     ProductReview43,
                     ProductReview44,
                     ProductReview45,
                     ProductReview46,
                     ProductReview47,
                     ProductReview48,
                     ProductReview49,
                     ProductReview50)
AllProducts
write.csv(AllProducts,"FiftyProductsReview.csv")
#view(AllProducts)
  
  
  



















```